---
title: "R package predict3d"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  fig.height=6,
  fig.width=6
)
```

R package `predict3d` aims to draw predicts plot for various regression models. The main two functions are ggPredict() for 2-dimensional plot and predict3d() for 3-dimensional plot.

# Package Installation

You can install the `predict3d` package from CRAN.

```{r,eval=FALSE}
install.packages("predict3d")
```


You can install the developmental version of `predict3d` package from github.

```{r,eval=FALSE}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("cardiomoon/predict3d"")
```

# Linear Regression Models

You can draw linear regression models. First model has one categorical and one continuous explanatory variables.

```{r,message=FALSE}
require(predict3d)
require(rgl)

fit1=lm(Sepal.Length~Sepal.Width*Species,data=iris)
ggPredict(fit1,digits=1)
```

You can draw plot for this model. ggPredict() function draws a scatterplot with regression line and shows regression equations parallel to the regression lines.

```{r}
ggPredict(fit1,digits=1)
```

Once you have create a model with predict3d(), you can rotate, zoom in and zoom out your object with your mouse.

The second model has two continuous variables as explanatory variables. You can change the labels and the relative x position and the y position.

```{r}
fit2=lm(mpg~wt*hp,data=mtcars)
ggPredict(fit2,xpos=c(0.3,0.5,0.5))
```

